Formalizing Stack Safety as a Security Property

### 2021-07-09 submission3/main.tex
More space

\subsection{Values and States}

@@

\subsection{Contexts}

@@

\subsection{Machine Traces}
\label{sec:traces}

@@

Next we consider {\em stepwise stack confidentiality}. Recall that our properties are
nested: we will quantify over subtraces that represent whole calls. For each such
subtrace, we will quantify over {\em variants} of its initial state. Then we require
that the original, {\em primary} traces move in {\em lockstep} with the variant.

@@

%\leo{I still don't know how to do this transition. Maybe contrast
%with the ``perhaps surprisingly'' later?} Note that
%similarity of observation traces could alternatively be defined coinductively,
%just like the prefix relation, but by dropping the asymmetric rules that allow
%for a finite trace ($\tau \lesssim \obsT$ or $w \lesssim w\obsT$).\apt{Is this immportant?}\leo{I agree. Probably not}

@@

Now we can inductively define the context update function; these rules again apply in the order
presented. \ifspace\bcp{Too much space between the second and third.}\fi

@@

\vspace*{-1ex}
\judgmentthree[ ReturnRec]
              {\(\mach,(\domMap,\rts) \stepsto_C \domMap',\rts'\)}
              {\(\domMap'' = \mathit{pop} ~ \domMap' ~ |\rts|\)}
              {\(\mach,(\domMap,\underscore::\rts) \stepsto_C \domMap'',\rts'\)}

>>>>

\paragraph*{Values and States}

@@

\paragraph*{Contexts}

@@

\paragraph*{Machine Traces}
\label{sec:traces}

@@

Next we consider {\em stepwise stack confidentiality}. Recall that our properties are
nested: we will quantify over subtraces that represent whole calls. For each
subtrace, we quantify over {\em variants} of its initial state. Then we require
that the original, {\em primary} traces move in {\em lockstep} with the variant.

@@

@@

Now we can inductively define the context update function, as before.

@@

\vspace*{-1ex}
\judgmenttwo[ ReturnRec]
              {\(\mach,(\domMap,\rts) \stepsto_C \domMap',\rts'\)}
              {\(\domMap'' = \mathit{pop} ~ \domMap' ~ |\rts|\)}
              {\(\mach,(\domMap,\underscore::\rts) \stepsto_C \domMap'',\rts'\)}
